\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-18 main.tex
Updates from Overleaf

%% Use the option review to obtain double line spacing
% \documentclass[preprint,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
\documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

@@

\newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
\newcommand{\SuperScreen}{\inline{SuperScreen}}

\newenvironment{code}{\captionsetup{type=listing}}{\hfill}
\SetupFloatingEnvironment{listing}{name=Code Block}
\BeforeBeginEnvironment{code}{\vspace{10pt}\begin{minipage}{\textwidth}}
\AfterEndEnvironment{code}{\end{minipage}}
\captionsetup[listing]{skip=0pt}

@@

\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        \underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:

\begin{equation}
    \label{eq:applied_to_stream}
    H_{z,\,\mathrm{applied}}(\vec{r})
    = -\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{equation}
where $\delta$ is the 2D Dirac delta function.

@@

\begin{equation}
    \label{eq:Heff}
    H_{z,\,\mathrm{eff},\,k}(\vec{r}) = -\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{equation}

@@

\begin{equation}
    \label{eq:Heff_sub}
    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = -\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'.
\end{equation}

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:applied_to_stream} as follows:

\begin{equation}
    \label{eq:applied_to_stream_vortices}
    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = -\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{equation}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to both an applied field and trapped vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

\begin{enumerate}
    \item{
        Calculate the stream function $g_\ell(\vec{r})$ for each layer $\ell$ by solving Eq.~\ref{eq:Heff_sub} given an applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$.
    }
    \item{
        For each layer $\ell$, calculate the $z$-component of the field due to the currents in all other layers $m\neq\ell$ (encoded in the stream function $g_m(\vec{r})$)
        using Eq.~\ref{eq:field_from_kernel}.
    }
    \item{
        Re-solve Eq.~\ref{eq:Heff_sub} taking the new applied field at each layer to be the original applied field plus the sum of screening fields from all other layers. This is accomplished via the substitution
        $$
            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
            + \sum_{m\neq\ell}
            \int_{F_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
        $$
        where $F_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
    }
    \item{
        Repeat steps 1-3 until the solution converges.
    }
\end{enumerate}

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:applied_to_stream}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $n$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. On the other hand, we denote element-wise multiplication with a dot: $(\mathbf{A}\cdot\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$. $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

@@

\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{\mathbf{Q}(\mathbf{g}\cdot\mathbf{w})}_\text{screening field}\\
    &=\mathbf{h}_{z,\,\mathrm{applied}}
    + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
    % h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top two lines) and the equivalent discrete sum version (bottom line).

@@

Once the stream function $\mathbf{g}$ is known for the full mesh,
the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}. Multiply-connected films and multi-layer structures are solved as described in Sections~\ref{section:model:holes} and \ref{section:model:multilayer} respectively.

@@

A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments. Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported (see Code Block~\ref{code:parameters}). \inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.

\begin{code}
\begin{minted}[fontsize=\small]{python}
from superscreen import Parameter

def f(x, y, a=1, b=0):
    return a * x**2 + b * y

param = Parameter(f, a=0, b=1)
print(param) # Parameter<f(a=0, b=1)>
other_param = Parameter(f, a=2, b=3)
print(other_param) # Parameter<f(a=2, b=3)>
print(param(0, 0) == f(0, 0, a=0, b=1)) # True
print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
param_squared = param ** 2
print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
) # True
\end{minted}
\captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates. Note that the positional arguments \inline{x} and \inline{y} can be either floating point scalars or 1-dimensional \inline{numpy} arrays.}
\label{code:parameters}
\end{code}

@@

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\SuperScreen                             & Set-theoretic  & Boolean   \\ \hline \hline
\inline{polygonA.union(polygonB)}        & $A\cup B$      & \inline{OR}      \\
\inline{polygonA.intersection(polygonB)} & $A\cap B$      & \inline{AND}     \\
\inline{polygonA.difference(polygonB)}   & $A\setminus B$ & \inline{AND NOT} \\
\inline{polygonA.difference(polygonB, symmetric=True)} & $(A\setminus B)\cup(B\setminus A)$ & \inline{XOR} \\ \hline
\end{tabular}
\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations. The vertices of \inline{polygonA} lie in set $A$ and the vertices of \inline{polygonB} lie in the set $B$. The object \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package.}
\label{table:polygon}
\end{table}

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
% See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

\begin{code}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
from superscreen.geometry import circle, box

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.5
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_triangles=8_000, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
solution.plot_fields()
solution.plot_currents()
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
\label{code:device}
\end{code}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
    \label{fig:ring-with-slit}
\end{figure}

\subsection{Solvers}
\label{section:overview:solvers}

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA. The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}. For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
%     \label{fig:square-ring-results}
% \end{figure}

@@

\begin{itemize}
    \item{
    \inline{superscreen.plot_streams()}: Given a \inline{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.

    See also: \inline{Solution.plot_streams()}.
    }
    \item{
    \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.

    See also: \inline{Solution.plot_currents()}.
    }
    \item{
    \inline{superscreen.plot_fields()}: Given a \inline{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.

    See also: \inline{Solution.plot_fields()}.
    }
    \item{
    \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z)$ or $H_z(x, y, z)$ at an arbitrary set of positions $(x, y, z)$.

>>>>

%% Use the option review to obtain double line spacing
% \documentclass[preprint,12pt]{elsarticle}
% \documentclass[preprint,3p,times,twocolumn]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
\documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

@@

\newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
\newcommand{\SuperScreen}{\inline{SuperScreen}}
\newcommand{\um}{\mu\mathrm{m}}

\newenvironment{code}{\captionsetup{type=listing}}{\hfill}
\SetupFloatingEnvironment{listing}{name=Code Block}
\BeforeBeginEnvironment{code}{\vspace{10pt}\begin{figure*}[t!]}
\AfterEndEnvironment{code}{\end{figure*}}
\captionsetup[listing]{skip=0pt}

@@

\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:

\begin{align}
\begin{split}
    \label{eq:applied_to_stream}
    &H_{z,\,\mathrm{applied}}(\vec{r})
    = \\ &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function.

@@

\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

@@

\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:

\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

\begin{enumerate}
    \item{
        Calculate the stream function $g_\ell(\vec{r})$ for each layer $\ell$ by solving Eq.~\ref{eq:applied_to_stream_vortices} given an applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$.
    }
    \item{
        For each layer $\ell$, calculate the $z$-component of the field due to the currents in all other layers $m\neq\ell$ (encoded in the stream function $g_m(\vec{r})$)
        using Eq.~\ref{eq:field_from_kernel}.
    }
    \item{
        Re-solve Eq.~\ref{eq:applied_to_stream_vortices} taking the new applied field at each layer to be the original applied field plus the sum of screening fields from all other layers. This is accomplished via the substitution
        \begin{align}
        \begin{split}
            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
            &\to H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)\\
            &+ \sum_{m\neq\ell}
            \int_{F_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
            \label{eq:iterative}
        \end{split}
        \end{align}
        where $F_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
    }
    \item{
        Repeat steps 1-3 until the solution converges.
    }
\end{enumerate}

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $n$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. On the other hand, we denote element-wise multiplication with a dot: $(\mathbf{A}\cdot\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$. $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

@@

\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{\mathbf{Q}(\mathbf{g}\cdot\mathbf{w})}_\text{screening field}\\
    &=\mathbf{h}_{z,\,\mathrm{applied}}
    + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top two lines) and the equivalent discrete sum version (bottom line).

@@

Once the stream function $\mathbf{g}$ is known for the full mesh,
the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}. Multi-layer structures are  iteratively as described in Section \ref{section:model:multilayer}.

@@

A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments. Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported. \inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.

% \begin{code}
% \begin{minted}[fontsize=\small]{python}
% from superscreen import Parameter

% def f(x, y, a=1, b=0):
%     return a * x**2 + b * y

% param = Parameter(f, a=0, b=1)
% print(param) # Parameter<f(a=0, b=1)>
% other_param = Parameter(f, a=2, b=3)
% print(other_param) # Parameter<f(a=2, b=3)>
% print(param(0, 0) == f(0, 0, a=0, b=1)) # True
% print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
% param_squared = param ** 2
% print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
% print(
%     (5 * param_squared / other_param)(5, 6)
%     == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
% ) # True
% \end{minted}
% \captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates. Note that the positional arguments \inline{x} and \inline{y} can be either floating point scalars or 1-dimensional \inline{numpy} arrays.}
% \label{code:parameters}
% \end{code}

@@

\begin{table*}
\centering
\begin{tabular}{|l|l|l|}
\hline
\SuperScreen                             & Set-theoretic  & Boolean   \\ \hline \hline
\inline{polygonA.union(polygonB)}        & $A\cup B$      & \inline{OR}      \\
\inline{polygonA.intersection(polygonB)} & $A\cap B$      & \inline{AND}     \\
\inline{polygonA.difference(polygonB)}   & $A\setminus B$ & \inline{AND NOT} \\
\inline{polygonA.difference(polygonB, symmetric=True)} & $(A\setminus B)\cup(B\setminus A)$ & \inline{XOR} \\ \hline
\end{tabular}
\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations. The vertices of \inline{polygonA} lie in set $A$ and the vertices of \inline{polygonB} lie in the set $B$. The object \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package.}
\label{table:polygon}
\end{table*}

@@

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
\begin{code}
\begin{minted}[fontsize=\small]{python}
import superscreen as sc
from superscreen.geometry import circle, box

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.5
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_triangles=8_000, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
solution.plot_fields()
solution.plot_currents()
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
\label{code:device}
\end{code}
Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles). In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.5\,\um$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
    \label{fig:ring-with-slit}
\end{figure*}

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\um$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA. The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}. For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
%     \label{fig:square-ring-results}
% \end{figure}

@@

\begin{itemize}
    \item{
    \inline{superscreen.plot_streams()}: Given a \inline{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.
    }
    \item{
    \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
    }
    \item{
    \inline{superscreen.plot_fields()}: Given a \inline{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.
    }
    \item{
    \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z)$ or $H_z(x, y, z)$ at an arbitrary set of positions $(x, y, z)$.
    }
\end{itemize}
